---
title: "xgb different approach"
author: "Bartosz Adamiec"
date: "17 02 2020"
output: github_document
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages('caret')
#install.packages('mlr')
library(dplyr)
library(lubridate)
library(ggplot2)
library(tidyverse)
library(kableExtra)
library(ggthemes)
library(corrplot)
library(data.table)
library(mlr)
library(xgboost)
```

```{r load_and_prep}
# xgboost

#environment preparation and data load
my_theme <- theme_fivethirtyeight() + theme(axis.title = element_text(), axis.title.x = element_text())

mydata_train <- read.csv("./train_set.csv", stringsAsFactors = FALSE, na.strings="")

mydata_test <- read.csv("./test_set.csv", stringsAsFactors = FALSE, na.strings="")

xgd_train <- mydata_train %>% select(playlist_genre, track_popularity, danceability, energy, key, loudness, mode, speechiness, acousticness, instrumentalness, liveness, valence, tempo, duration_ms)

xgd_test <- mydata_test %>% select(playlist_genre, track_popularity, danceability, energy, key, loudness, mode, speechiness, acousticness, instrumentalness, liveness, valence, tempo, duration_ms)



xgd_train <- xgd_train %>% mutate_if(is.character,as.factor)
xgd_test <- xgd_test %>% mutate_if(is.character,as.factor)


xgd_train$duration_ms <- scale(xgd_train$duration_ms)
xgd_test$duration_ms <- scale(xgd_test$duration_ms)



str(xgd_train)

